How to Avoid OOTA Without Really Trying

### 2024-10-03 paper/ootavacuous.tex
ootavacuous: Reorder and reword new sections 2.2.7 and 2.2.8
Which were originally 2.2.3 and 2.2.8.

Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\subsubsection{Non-Deterministic Semantic Dependencies}
\label{sec:Non-Deterministic Semantic Dependencies}

Compiler optimizers also exploit the nondeterministic aspects of an
execution.
Consider this example, with \co{i} initially zero:
\begin{quote}
\begin{verbatim}
int foo(int a, int b)
{
   return a / b;
}

@@

\subsubsection{Per-Architecture Dependent Semantic Dependencies}
\label{sec:Per-Architecture Dependent Semantic Dependencies}

The implementation-defined aspects of the standard permit architectures to
differ as to whether an abstract execution contains a semantic dependency.
For example, consider the following, where the type of \co{c} is \co{char}:
\begin{quote}
\begin{verbatim}
y = (c >= 0);
\end{verbatim}
\end{quote}
Here \co{y} is semantically dependent on \co{c} in executions
running on implementations in
which \co{char} is a signed type,
but not those for which it is unsigned.

@@

The C++ standard describes the execution of a program in terms of
``a parameterized nondeterministic abstract machine'' in 4.1.2p1
(\co{[intro.abstract]}).
This description specifies how the abstract machine carries out the
operations of a source program in great, but not complete, detail:
\begin{itemize}
\item	Some of the abstract machine's characteristics are
	implementation defined, including things like the number of
	bits in the various integer types
	or whether the \co{char} type is signed (see
	Section~\ref{sec:Per-Architecture Dependent Semantic Dependencies}).
\item	Some aspects of an execution are unspecified or nondeterministic,
	including things like the order of evaluation of the operands
	of most binary operators or of the arguments in a function call.
	Implementations may choose from a set of allowed behaviors
	(see
	Section~\ref{sec:Non-Deterministic Semantic Dependencies}).
\item	Some actions are deemed to have undefined results; the standard
	says essentially nothing about programs that can give rise to
	undefined behavior.
\item	Asynchronous actions (i.e., signal handlers) are largely ignored.
\item	Input and output are not described in any detail.
\end{itemize}
In addition to these points, the standard does not specify which store
an atomic load must read from, beyond requiring that the overall
pattern of loads and stores be consistent with the C++ memory model.
In short, the standard grants C++ implementations considerable freedom,
as detailed in
Section~\ref{sec:C++ Compilers}.

>>>>

@@

\subsubsection{Semantic Dependencies and Free Choices}
\label{sec:Semantic Dependencies and Free Choices}

Consider the following example, with variable \co{i} initially zero:
\begin{quote}
\begin{verbatim}
int foo(int a, int b)
{
   return a / b;
}

\subsubsection{Semantic Dependencies and Architectural Variations}
\label{sec:Semantic Dependencies and Architectural Variations}

In some cases, the standard permits architectures to differ as to whether
an abstract execution contains a semantic dependency.
For example, consider the following, where the type of \co{c} is \co{char}:
\begin{quote}
\begin{verbatim}
y = (c >= 0);
\end{verbatim}
\end{quote}
Here \co{y} is semantically dependent on \co{c} in executions
running on implementations in
which \co{char} is a signed type,
but not those for which it is unsigned.

@@

The C++ standard describes the execution of a program in terms of
``a parameterized nondeterministic abstract machine'' in 4.1.2p1
(\co{[intro.abstract]}).
This description specifies how the abstract machine carries out the
operations of a source program in great, but not complete, detail:
\begin{itemize}
\item	Some of the abstract machine's characteristics are
	implementation defined, including things like the number of
	bits in the various integer types
	or whether the \co{char} type is signed (see
	Section~\ref{sec:Semantic Dependencies and Architectural Variations}).
\item	Some aspects of an execution are unspecified or nondeterministic,
	including things like the order of evaluation of the operands
	of most binary operators or of the arguments in a function call.
	Implementations may choose from a set of allowed behaviors
	(see
	Section~\ref{sec:Semantic Dependencies and Free Choices}).
\item	Some actions are deemed to have undefined results; the standard
	says essentially nothing about programs that can give rise to
	undefined behavior.
\item	Asynchronous actions (i.e., signal handlers) are largely ignored.
\item	Input and output are not described in any detail.
\end{itemize}
In addition to these points, the standard does not specify which store
an atomic load must read from, beyond requiring that the overall
pattern of loads and stores be consistent with the C++ memory model.
In short, the standard grants C++ implementations considerable freedom,
as detailed in
Section~\ref{sec:C++ Compilers}.
